Characterizing Stellar Streams by ML

### 2023-08-14 src/tex/ms.tex
[showyourwork] overleaf sync

        \subsubsection{Bounding Boxes}

@@

        We generate synthetic observations by sampling points from a third degree polynomial \JN{check this} with a constant scatter. Density variations are then simulated by evaluating the stream density with two Gaussian distributions centered at different values of $\phi_1$ with random amplitudes (which sum to $1$) and widths. Stream stars are then removed using random sampling, weighted by their likelihood of belonging to the density. The background astrometric  points in are generated from exponential distributions at each $\phi_1$. The number of stream stars is \variable{mock/nstream_variable.txt}, while the number of background stars is \JN{Y}.

@@

            \variable{output/gd1_select_members.tex}

>>>>

        \subsubsection{Parameter Bounds}

            We implement a hard bound on the range of all parameters.

@@

        We generate synthetic observations by sampling points from a third degree polynomial \JN{check this} with a constant scatter. Density variations are then simulated by evaluating the stream density with two Gaussian distributions centered at different values of $\phi_1$ with random amplitudes (which sum to $1$) and widths. Stream stars are then removed using random sampling, weighted by their likelihood of belonging to the density. The background astrometric  points in are generated from exponential distributions at each $\phi_1$. The number of stream stars is $\variable{output/mock/nstream_variable.txt}$, while the number of background stars is $\variable{output/mock/nbackground_variable.txt}$.

@@

            \variable{output/gd1/select_members.tex}
